{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-05-08 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, new stuff

        Most literatures overcomplicate the proofs and the matters regarding FISTA algorithm and its convergence rate. 

@@

                \Vert \mathcal G_{L_k} (y_k)\Vert &\le 

@@

        \begin{theorem}[specialized GMAPG convergence rate]

@@

>>>>

        We make the proofs for FISTA  with common enhancement technique available in simple proofs. 

@@

                \Vert \mathcal G_{1/L_k} (y_k)\Vert &\le 

@@

        \begin{theorem}[specialized GMAPG convergence rate]\label{thm:gmapg-specialized-convergence}
            Suppose that $F = f + g$ satisfy Assumption \ref{ass:standard-fista}. 
            Let the sequence $(x_k, v_k, v_k)$ satisfy GMAPG, definition \ref{def:generic-mapg-ls} and, assume that the GMAPG is initialized by $x_0 = v_0 = T_{1/L_0}(x_{-1})$ and, assume $\rho_{k - 1} = L_{k}^{-1}L_{k}$, $\alpha_0 = 1$ so the sequence $(\alpha_k)_{k \ge 0}$ satisfies for all $k\ge 1$: $\alpha_{k - 1}^2L_k^{-1}L_{k - 1}(1 - \alpha_k) = \alpha_k^2$. 
            Let $x^+$ be a minimizer of $F$, define 
                \hat L_k = \max\left(
                    L_0, \frac{1}{k}\sum_{i = 1}^{k} \sqrt{L_i^{-1}}
            Then, we have convergence claim: 
                \item \begin{align*}
                    F(x_k) - F(x^+) + \frac{L_k\alpha_k}{2}\Vert x^+ - v_k\Vert^2 \le 
                    \frac{2\hat L_k}{(2 + k)^2}\Vert x^+ - x_{-1}\Vert^2.
                \item 
                    \Vert \mathcal G_{1/L_k}(y_k)\Vert \le 
                    \frac{2\hat L_k L_k}{2 + k}
                        1 - L_k^{-1/2}L_{k - 1}^{1/2}
                    \Vert x^+ - v_0\Vert. 

@@

            To see (i), use \ref{lemma:gmapg-seq-bnd} and the remark with Theorem \ref{thm:gmapg-ls-convergence} because the assumptions of $x^+, (\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is the same. 
            To see (ii), the convergence claim from \ref{thm:gmapg-generic-gradmap-convergence} simplifies with $\hat L_k \ge L_0$ and, it has 
                \Vert \mathcal G_{1/L_k}(y_k) \Vert
                    \frac{2\sqrt{\hat L_kL_0}L_k}{2 + k}
                    1 + \min(\rho_{k - 1}, L_k^{-1}L_{k - 1})^{1/2}
                    \frac{2\sqrt{\hat L_kL_0}L_k}{2 + k}
                    1 + L_k^{-1/2}L_{k - 1}^{1/2}
                    \frac{2\hat L_k L_k}{2 + k}
                    1 + L_k^{-1/2}L_{k - 1}^{1/2}
